% ================================================================
\section{Conclusion}
% ================================================================

We presented Completus, an end-to-end pipeline for fine-tuning and
locally serving a 1.5B-parameter code model on a single consumer GPU.
Starting from CodeSearchNet, we assembled a curated bilingual training
corpus covering Python and Go, applying deduplication, smell
filtering, and a fill-in-the-middle data transform. One epoch of
QLoRA fine-tuning on an 8\,GB GPU raises HumanEval pass@1 from 10.98\%
to 42.68\% under a deployment-faithful zero-shot protocol, a 31.7
percentage-point gain over the untuned base in the format used for
local serving. The merged adapter is quantised to GGUF q4\_k\_m and
registered with Ollama, providing a fully local code completion
endpoint served entirely on consumer hardware.

Future work will evaluate the Go model on HumanEval-X, explore longer
fine-tuning schedules and larger rank budgets, and assess multi-file
context completion in realistic, project-level scenarios.

% ================================================================
\section*{Acknowledgement}
% ================================================================

The authors thank the open-source communities behind Unsloth, Ollama,
and the HuggingFace ecosystem.

\paragraph{Data Availability.}
Code and Modelfiles are available at
\url{https://github.com/kadusic1/completus}. Training data is derived
from CodeSearchNet~\cite{Husain2019CSN}, publicly available on
HuggingFace.

\paragraph{Author Contributions.}
N.~Smajlovi\'{c}: data curation, methodology, software (evaluation,
Windows compatibility), writing (original draft, related work).
A.~Kadu\v{s}i\'{c}: conceptualisation, software (training, merge and
export pipeline), validation, writing (review and editing).

\paragraph{Conflict of Interest.}
The authors declare no conflict of interest.

\paragraph{AI Usage Disclosure.}
Claude (Anthropic) was used as an AI coding assistant during
development and for drafting portions of this manuscript. All results
and final content were verified and approved by the authors.
