% ================================================================
\section{Introduction}
% ================================================================

Modern code language models such as GPT-4.1 and Claude Sonnet deliver
impressive autocompletion quality, but they require a persistent
internet connection, expose source code to third-party servers, and
incur per-token costs that compound over a workday. These constraints
limit adoption in regulated industries, air-gapped environments, and
resource-constrained settings. A locally running model that completes
code without any network call would close this gap---if it can be made
small enough to fit on consumer hardware while remaining useful.

Parameter-efficient fine-tuning (PEFT) has made it practical to
specialise large pretrained models at a fraction of the cost of full
fine-tuning~\cite{Hu2021LoRA, Dettmers2023QLoRA}. Quantisation
formats such as GGUF, served through runtimes such as Ollama, allow
merged adapter weights to run efficiently on consumer
GPUs~\cite{Kurt2026Quant}. The combination suggests a concrete recipe:
take a compact, permissively licensed code model, fine-tune it with
QLoRA on domain data, merge and quantise the result, and expose it
through a local API on the developer's own machine.

This paper describes Completus, an end-to-end implementation of that
recipe. Our contributions are:
\begin{itemize}[leftmargin=14.4pt]
  \item A curated preprocessing pipeline over
        CodeSearchNet~\cite{Husain2019CSN} covering Python and Go,
        applying deduplication, smell filtering, docstring-quality
        filtering, and a fill-in-the-middle (FIM) transform.
  \item A reproducible QLoRA fine-tuning procedure for
        Qwen2.5-Coder-1.5B~\cite{Hui2024Qwen25} using a fixed-rank
        LoRA adapter~\cite{Hu2021LoRA} that runs on an 8\,GB GPU in
        about one to two hours per language.
  \item An empirical evaluation showing that one epoch of fine-tuning
        raises HumanEval pass@1 from 10.98\% to 42.68\% under a
        deployment-faithful zero-shot protocol, a statistically
        significant gain over the untuned base under identical
        conditions.
  \item A packaging step that exports the merged model to GGUF
        q4\_k\_m and registers it with Ollama for fully local
        inference.
\end{itemize}
