\begin{thebibliography}{00}

\bibitem{Vaswani2017Attention}
A.~Vaswani, N.~Shazeer, N.~Parmar, J.~Uszkoreit, L.~Jones,
A.~N.~Gomez, L.~Kaiser, and I.~Polosukhin,
``Attention is all you need,''
\textit{arXiv preprint}, arXiv:1706.03762, 2017.

\bibitem{Hu2021LoRA}
E.~J.~Hu, Y.~Shen, P.~Wallis, Z.~Allen-Zhu, Y.~Li, S.~Wang,
L.~Wang, and W.~Chen,
``LoRA: Low-rank adaptation of large language models,''
\textit{arXiv preprint}, arXiv:2106.09685, 2021.

\bibitem{Dettmers2023QLoRA}
T.~Dettmers, A.~Pagnoni, A.~Holtzman, and L.~Zettlemoyer,
``QLoRA: Efficient finetuning of quantized LLMs,''
\textit{arXiv preprint}, arXiv:2305.14314, 2023.

\bibitem{Zhang2023AdaLoRA}
Q.~Zhang, M.~Chen, A.~Bukharin, P.~He, Y.~Cheng, W.~Chen,
and T.~Zhao,
``AdaLoRA: Adaptive budget allocation for parameter-efficient
fine-tuning,''
\textit{arXiv preprint}, arXiv:2303.10512, 2023.

\bibitem{Weyssow2023PEFT}
M.~Weyssow, X.~Zhou, K.~Kim, D.~Lo, and H.~Sahraoui,
``Exploring parameter-efficient fine-tuning techniques for code
generation with large language models,''
\textit{arXiv preprint}, arXiv:2308.10462, 2023.

\bibitem{Han2024PEFTSurvey}
Z.~Han, C.~Gao, J.~Liu, J.~Zhang, and S.~Q.~Zhang,
``Parameter-efficient fine-tuning for large models: A comprehensive
survey,''
\textit{arXiv preprint}, arXiv:2403.14608, 2024.

\bibitem{Hui2024Qwen25}
B.~Hui, J.~Yang, Z.~Cui et al.,
``Qwen2.5-Coder technical report,''
\textit{arXiv preprint}, arXiv:2409.12186, 2024.

\bibitem{Roziere2023CodeLlama}
B.~Rozi\`{e}re, J.~Gehring, F.~Gloeckle et al.,
``Code Llama: Open foundation models for code,''
\textit{arXiv preprint}, arXiv:2308.12950, 2023.

\bibitem{Guo2024DeepSeek}
D.~Guo, Q.~Zhu, D.~Yang et al.,
``DeepSeek-Coder: When the large language model meets
programming---the rise of code intelligence,''
\textit{arXiv preprint}, arXiv:2401.14196, 2024.

\bibitem{Li2023StarCoder}
R.~Li, L.~Ben Allal, Y.~Zi et al.,
``StarCoder: May the source be with you!,''
\textit{arXiv preprint}, arXiv:2305.06161, 2023.

\bibitem{Husain2019CSN}
H.~Husain, H.-H.~Wu, T.~Gazit, M.~Allamanis, and
M.~Brockschmidt,
``CodeSearchNet challenge: Evaluating the state of semantic code
search,''
\textit{arXiv preprint}, arXiv:1909.09436, 2019.

\bibitem{Bavarian2022FIM}
M.~Bavarian, H.~Jun, N.~Tezak, J.~Schulman, C.~McLeavey,
J.~Tworek, and M.~Chen,
``Efficient training of language models to fill in the middle,''
\textit{arXiv preprint}, arXiv:2207.14255, 2022.

\bibitem{Xue2025CleanCode}
Z.~Xue, X.~Zhang, Z.~Gao, X.~Hu, S.~Gao, X.~Xia, and S.~Li,
``Clean code, better models: Enhancing LLM performance with
smell-cleaned dataset,''
\textit{arXiv preprint}, arXiv:2508.11958, 2025.

\bibitem{Lee2021Dedup}
K.~Lee, D.~Ippolito, A.~Nystrom, C.~Zhang, D.~Eck,
C.~Callison-Burch, and N.~Carlini,
``Deduplicating training data makes language models better,''
\textit{arXiv preprint}, arXiv:2107.06499, 2021.

\bibitem{Luo2023WizardCoder}
Z.~Luo, C.~Xu, P.~Zhao, Q.~Sun, X.~Geng, W.~Hu, C.~Tao,
J.~Ma, Q.~Lin, and D.~Jiang,
``WizardCoder: Empowering code large language models with
Evol-Instruct,''
\textit{arXiv preprint}, arXiv:2306.08568, 2023.

\bibitem{Kurt2026Quant}
U.~Kurt,
``Which quantization should I use? A unified evaluation of
llama.cpp quantization on Llama-3.1-8B-Instruct,''
\textit{arXiv preprint}, arXiv:2601.14277, 2026.

\end{thebibliography}
